### 2013-07-23 doc/asplos14/intro.tex
fixed bib references

\vspace{0.5ex}
\noindent{\bf Poor data locality and frequent communication.} Data reference patterns of irregular applications are unpredictable and tend to be spread across the entire system. This results in frequent requests for small pieces of remote data. Caches are of little assistance because of low temporal and spatial locality. Prefetching is of limited value because request locations are not known early enough. Data-parallel frameworks such as MapReduce~\cite{mapreduce:osdi04} are ineffective because they rely on effective data partitioning and regular communication patterns. Consequently, commodity networks, which are designed for large packets, achieve just a fraction of their peak bandwidth on small messages, starving application performance.

>>>>

\vspace{0.5ex}
\noindent{\bf Poor data locality and frequent communication.} Data reference patterns of irregular applications are unpredictable and tend to be spread across the entire system. This results in frequent requests for small pieces of remote data. Caches are of little assistance because of low temporal and spatial locality. Prefetching is of limited value because request locations are not known early enough. Data-parallel frameworks such as MapReduce~\cite{Dean:2008:MSD:1327452.1327492} are ineffective because they rely on effective data partitioning and regular communication patterns. Consequently, commodity networks, which are designed for large packets, achieve just a fraction of their peak bandwidth on small messages, starving application performance.
